% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Mon Sep 23 15:40:52 2024
\begingroup\fontsize{8pt}{10pt}\selectfont
\begin{longtable}{|p{0.15\textwidth}|p{0.10\textwidth}|p{0.5\textwidth}|p{0.07\textwidth}|p{0.10\textwidth}|}
\caption{Definition of the variables includes in each data file.} \\ 
  \hline
{\textbf{Data.set.file}} & {\textbf{Variable.identity}} & {\textbf{Variable.definition}} & {\textbf{Units}} & {\textbf{Storage.type}} \\ 
  \hline
BYLOT-species\_taxonomy.csv & functional\_group & Functional group for each species. The classification of species into functional groups is based on Moisan et al. (2023). &  & string \\ 
   \hline
BYLOT-species\_taxonomy.csv & scientific\_name & Bird scientific names were obtained from the IOC World Bird List 14.2 (Gill et al., 2024). Mammal scientific names were obtained from the Mammal species of the world: a taxonomic and geographic reference (Wilson, 2005). However, we considered here Mustela erminea richardsonii as Mustela richardsonii due to recent genetic analysis (Colella et al., 2021). &  & string \\ 
   \hline
BYLOT-species\_taxonomy.csv & species & Common species english name. &  & string \\ 
   \hline
BYLOT-species\_taxonomy.csv & annual\_cycle\_strategy & Annual cycle strategy of each species (i.e., resident, partially migratory or migratory). The classification of species annual cycle strategy is based on Gauthier et al., (2011)  and Moisan et al. (2023). &  & string \\ 
   \hline
BYLOT-species\_abundance.csv & species & Common species english name. &  & string \\ 
   \hline
BYLOT-species\_abundance.csv & year & Year corresponding to the estimate of annual abundance. & years & integer \\ 
   \hline
BYLOT-species\_abundance.csv & status & Reproductive status of the individuals (i.e., undetermined or breeding). &  & string \\ 
   \hline
BYLOT-species\_abundance.csv & method & Brief overview of the method used to estimate the species abundance. &  & string \\ 
   \hline
BYLOT-species\_abundance.csv & abundance & Estimate of the annual number of individuals found within the 389 km2 study area located on the southern part of Bylot Island during the breeding season (May to August). This includes both breeding and non-breeding individuals that stay in the study area for a significant period of time, and excludes non-breeding individuals that stop for only a few days during their migration. The estimates only consider adults, with the exception of lemmings, for which no distinction has been made between juveniles and adults. & individuals & integer \\ 
   \hline
BYLOT-mean\_species\_abundance.csv & species & Common species english name. &  & string \\ 
   \hline
BYLOT-mean\_species\_abundance.csv & method & Brief overview of the method used to estimate the species abundance. &  & string \\ 
   \hline
BYLOT-mean\_species\_abundance.csv & mean\_abundance & Estimate of the mean annual number of individuals found within the 389 km2 study area located on the southern part of Bylot Island during the breeding season (May to August). This includes both breeding and non-breeding individuals that stay in the study area for a significant period of time, and excludes non-breeding individuals that stop for only a few days during their migration. The estimates only consider adults, with the exception of lemmings, for which no distinction has been made between juveniles and adults. & individuals & integer \\ 
   \hline
BYLOT-mean\_species\_abundance.csv & sd\_abundance & Standard deviation of the annual species abundance. & individuals & numeric \\ 
   \hline
BYLOT-mean\_species\_abundance.csv & sample\_size\_abundance & Number of years consider in the calculation of mean annual abundance. & years & integer \\ 
   \hline
BYLOT-mean\_species\_body\_mass.csv & species & Common species english name. &  & string \\ 
   \hline
BYLOT-mean\_species\_body\_mass.csv & source & Source from which estimate were derived (i.e., measurements from the study area or  extracted from Wilman et al. 2014). &  & string \\ 
   \hline
BYLOT-mean\_species\_body\_mass.csv & body\_mass\_g & Mean individual body mass. & grams & numeric \\ 
   \hline
BYLOT-interannual\_variation\_nest\_density.csv & species & Common species english name. &  & string \\ 
   \hline
BYLOT-interannual\_variation\_nest\_density.csv & zone & Sampled zone of the study area (see figure 2 and 3). &  & string \\ 
   \hline
BYLOT-interannual\_variation\_nest\_density.csv & mean\_nest\_density\_km2 & Estimate of the mean annual nest density measured within the corresponding zone
of the study area. & nests per square kilometer & numeric \\ 
   \hline
BYLOT-interannual\_variation\_nest\_density.csv & sd\_nest\_density\_km2 & Standard deviation of the annual nest density measured within the corresponding
zone of the study area. & nests per square kilometer & numeric \\ 
   \hline
BYLOT-interannual\_variation\_nest\_density.csv & sample\_size\_nest\_density\_km2 & Number of years consider in the calculation of the nest density. & years & integer \\ 
   \hline
\hline
\label{table:summary_variables}
\end{longtable}
\endgroup
